\sysfull

### 2018-04-17 paper/paging.tex
reduced algorithms

\begin{algorithm}[t]
	\caption{\texttt{RP}(variable $v$)}
	\label{algo:rwar}
	\scriptsize
	%\small
	\begin{algorithmic}[1]
		\State $t \leftarrow \Call{GetTag}{v}$ 
        \State $i \gets \{ j\ |\ \Call{GetTag}{\texttt{working}[j]} = t \}$ \Comment{Look in the page buffer}
		\If { $i = \emptyset$ } \Comment{Is the variable in a resident page?}
		\State	$i \gets \Call{PageFault}{t}$ \Comment{Page in from non-volatile memory}
		\EndIf
		\State $o \leftarrow \Call{GetOffset}{v}$ 		
		\State \Return \texttt{working}[$i$][$o$]  \Comment{Return directly from page buffer}
	\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}
	\caption{\texttt{PageFault}(tag $t$)}
	\label{algo:pagefault}
	\scriptsize
	%\small
	\begin{algorithmic}[1]
        \State \LeftComment{$i_\text{victim}$: volatile index to next free slot or page to be evicted, set to 0 at boot}
        \State \LeftComment{\texttt{\underline{shadowCount}}: non-volatile, reset to 0 on boot unless in phase 2 commit}
        \State $t_\text{victim} \gets \Call{Tag}{\texttt{working}[i_\text{victim}]}$
		\If {\Call{isDirty}{working[$i_\text{victim}$]} }	\Comment{Are we evicting a dirty page?}
		\State $\texttt{\underline{shadow}}[t_\text{victim}] \xleftarrow{\text{DMA}} \texttt{working}[i_\text{victim}]$
            \Comment{Swap out the page}
        \If {$t_\text{victim} \not\in \texttt{\underline{shadowList}}$} \Comment{Keep track as list for quick traversal}
            \State $\texttt{\underline{shadowList}}[\texttt{shadowCount++}] \gets t_\text{victim}$
        \EndIf
		\EndIf
		\If {\Call{exists}{\underline{shadow}[$t$]}} \Comment{Had the page been swapped out earlier?}
		\State $\texttt{working}[i_\text{victim}] \xleftarrow{\text{DMA}} \texttt{\underline{shadow}}[t]$
            \Comment{Get page from commit buffer}
		\Else
		\State $\texttt{working}[i_\text{victim}] \xleftarrow{\text{DMA}} \texttt{\underline{store}}[t]$
            \Comment{Get page from backing store}
		\EndIf 
        \State $i_\text{victim} \gets (i_\text{victim} + 1) \mod |\texttt{pageBufLength}|$ \Comment{FIFO eviction policy}
	\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}[t]
	\caption{Two-phase commit}
	\label{algo:commit}
	\scriptsize
	%\small
	\begin{algorithmic}[1]
        \Procedure{CommitPhase1}{} \Comment{Invoked from \texttt{next\_task} on last coalesced task}
            \For {$i \in 0..|\texttt{working}|-1$}
                \State $t \gets \Call{Tag}{\texttt{working}[i]}$
                \State $\texttt{\underline{shadow}}[\Call{Tag}{\texttt{working}[i]}] \xleftarrow{\text{DMA}} \texttt{working}[i]$
                \State $\texttt{\underline{shadowList}}[\texttt{\underline{shadowCount}}] \gets t$
                \State $\texttt{\underline{shadowCount}} \gets \texttt{\underline{shadowCount}} + 1$
            \EndFor
            \State \Call{CommitPhase2}{}
        \EndProcedure
        \Procedure{CommitPhase2}{}
            \State $\texttt{\underline{committing}} \gets \textbf{true}$
            \While{\texttt{\underline{commitIndex}} < \texttt{\underline{shadowCount}}} \Comment{\texttt{\underline{commitIndex}} set to 0 at first boot}
                \State $t \gets \texttt{\underline{shadowList}}[\texttt{\underline{commitIndex}}]$
                \State \Call{commitToStore}{\texttt{\underline{shadow}}[t]}
                \State $\texttt{\underline{commitIndex}} \gets \texttt{\underline{commitIndex}} + 1$
            \EndWhile
            \State $\texttt{\underline{shadowCount}} \gets 0$
            \State $\texttt{\underline{commitIndex}} \gets 0$
            \State $\texttt{\underline{committing}} \gets \textbf{false}$
        \EndProcedure
        \Procedure{OnBoot}{} \Comment{Invoked on every boot, before transitioning to a task}
            \If { \texttt{\underline{committing}} } \Call{CommitPhase2}{}
            \EndIf 
            \State $\texttt{\underline{shadowCount}} \gets 0$, $i_\text{victim} \gets 0$
        \EndProcedure
	\end{algorithmic}
\end{algorithm}

>>>>

%\begin{algorithm}[t]
\begin{wrapfigure}{t}{0.4\textwidth}
\fbox{\parbox{\linewidth}{
	\captionof{algorithm}{\texttt{RP}(variable $v$)}
	\label{algo:rwar}
	\scriptsize
	%\small
	\begin{algorithmic}[1]
		\State $t \leftarrow \Call{GetTag}{v}$ 
        \State $i \gets \{ j\ |\ \Call{GetTag}{\texttt{working}[j]} = t \}$ \Comment{Search page}
		\If { $i = \emptyset$ } \Comment{Var in a resident page?}
		\State	$i \gets \Call{PageFault}{t}$ \Comment{Swap page in}
		\EndIf
		\State $o \leftarrow \Call{GetOffset}{v}$ 		
		\State \Return \texttt{working}[$i$][$o$]  \Comment{Return from page}
%	\end{algorithmic}
%\end{algorithm}
	\end{algorithmic}}}
\end{wrapfigure}

@@

%\begin{algorithm}
\begin{wrapfigure}{t}{0.5\textwidth}
\fbox{\parbox{\linewidth}{
	\captionof{algorithm}{\texttt{PageFault}(tag $t$)}
	\label{algo:pagefault}
	\scriptsize
	%\small
	\begin{algorithmic}[1]
        \State \LeftComment{$i_\text{victim}$: index to free slot or page to be evicted, initially 0}
        \State \LeftComment{\texttt{\underline{shadowCount}}: non-volatile, 0 on boot unless in phase 2 commit}
        \State $t_\text{victim} \gets \Call{Tag}{\texttt{working}[i_\text{victim}]}$
		\If {\Call{isDirty}{working[$i_\text{victim}$]} }	\Comment{Evicting a dirty page?}
		\State $\texttt{\underline{shadow}}[t_\text{victim}] \xleftarrow{\text{DMA}} \texttt{working}[i_\text{victim}]$
            \Comment{Swap out the page}
        \If {$t_\text{victim} \not\in \texttt{\underline{shadowList}}$} \Comment{Keep track for quick traversal}
            \State $\texttt{\underline{shadowList}}[\texttt{shadowCount++}] \gets t_\text{victim}$
        \EndIf
		\EndIf
		\If {\Call{exists}{\underline{shadow}[$t$]}} \Comment{Page swapped out earlier?}
		\State $\texttt{working}[i_\text{victim}] \xleftarrow{\text{DMA}} \texttt{\underline{shadow}}[t]$
            \Comment{Get from commit buffer}
		\Else
		\State $\texttt{working}[i_\text{victim}] \xleftarrow{\text{DMA}} \texttt{\underline{store}}[t]$
            \Comment{Get from backing store}
		\EndIf 
        \State $i_\text{victim} \gets (i_\text{victim} + 1) \mod |\texttt{pageBufLength}|$ \Comment{FIFO evict}
%	\end{algorithmic}
%\end{algorithm}
	\end{algorithmic}}}
\end{wrapfigure}

@@

%\begin{algorithm}[t]
\begin{wrapfigure}{t}{0.5\textwidth}
\fbox{\parbox{\linewidth}{
	\captionof{algorithm}{\texttt{PageFault}(tag $t$)}
	\caption{Two-phase commit}
	\label{algo:commit}
	\scriptsize
	%\small
	\begin{algorithmic}[1]
        \Procedure{CommitPhase1}{} \Comment{On last coalesced task}
            \For {$i \in 0..|\texttt{working}|-1$}
                \State $t \gets \Call{Tag}{\texttt{working}[i]}$
                \State $\texttt{\underline{shadow}}[\Call{Tag}{\texttt{working}[i]}] \xleftarrow{\text{DMA}} \texttt{working}[i]$
                \State $\texttt{\underline{shadowList}}[\texttt{\underline{shadowCount}}] \gets t$
                \State $\texttt{\underline{shadowCount}} \gets \texttt{\underline{shadowCount}} + 1$
            \EndFor
            \State \Call{CommitPhase2}{}
        \EndProcedure
        \Procedure{CommitPhase2}{} \Comment{\texttt{\underline{commitIndex}} 0 on first boot}
            \State $\texttt{\underline{committing}} \gets \textbf{true}$
            \While{\texttt{\underline{commitIndex}} < \texttt{\underline{shadowCount}}}
                \State $t \gets \texttt{\underline{shadowList}}[\texttt{\underline{commitIndex}}]$
                \State \Call{commitToStore}{\texttt{\underline{shadow}}[t]}
                \State $\texttt{\underline{commitIndex}} \gets \texttt{\underline{commitIndex}} + 1$
            \EndWhile
            \State $\texttt{\underline{shadowCount}} \gets 0$
            \State $\texttt{\underline{commitIndex}} \gets 0$
            \State $\texttt{\underline{committing}} \gets \textbf{false}$
        \EndProcedure
        \Procedure{OnBoot}{} \Comment{Invoked on every boot}
            \If { \texttt{\underline{committing}} } \Call{CommitPhase2}{}
            \EndIf 
            \State $\texttt{\underline{shadowCount}} \gets 0$, $i_\text{victim} \gets 0$
        \EndProcedure
%	\end{algorithmic}
%\end{algorithm}
	\end{algorithmic}}}
\end{wrapfigure}
